Wu-Tang Clan

### 2015-03-20 rmtw/a6/latex8.tex
sadsa
Added first draft of Data Collection

\subsection{Data Collection}
• data collection procedures (e.g. interviews? survey? and sampling?) 
The main form of data collection will be performed through code and documentation analysis (third degree aka independent). In addition to this analysis, interviews will be conducted. The main purpose of the interviews is to provide insight regarding RQ1.1, but also to support data triangulation.

Explain how we will sample the interviewees. (Ask Imed how this will be done).

It is importnat that we explain exactly why we chose the collection methods we did. It is also important htat we clearly explain which methods relate to which RQs.

Also explain why for example questionnaire wasn't used.

>>>>

\subsection{Data Collection}
% • data collection procedures (e.g. interviews? survey? and sampling?) 
% The main form of data collection will be performed through code and documentation analysis (third degree aka independent). In addition to this analysis, interviews will be conducted. The main purpose of the interviews is to provide insight regarding RQ1.1, but also to support data triangulation.

% Explain how we will sample the interviewees. (Ask Imed how this will be done).

% It is importnat that we explain exactly why we chose the collection methods we did. It is also important htat we clearly explain which methods relate to which RQs.

% Also explain why for example questionnaire wasn't used.

% Interviews will be used for:
% Main: Verify our findings
% Sub1: Provide additional insight (find stuff we missed)
% SUb2: Get more info about the user of the api

The data were collected primarily through third degree methods, such as first hand inspections of the source code and the archival analysis of relating documentation. From the source code we extracted information regarding the public facing APIs. Specifically, we collected information about return types, parameters and method names. The data were collected from both versions of the APIs, with the changes between the two versions being of particular interest. From the archival documentation we collected information regarding the intent behind the functionality in API calls. For example, we examined differences in descriptions of methods prior to and after return types or parameters were renamed. This information provided insight into the motivation behind the changes.

These collection methods were the most appropriate given that the data were readily available from the company. This did bring with it concerns that the data were not collected for the purpose of research \cite{!!! host}, meaning that some of the data had the risk of being irrelevant and that erroneous data had the potential to exist. Collection from another techniques were required to fill in the missing data.

A first degree interview was also be conducted after the initial source inspections had taken place. The main purpose was to validate our findings with the architects of the API. Furthermore, the interviews provided additional insight into decisions and motivations behind changes that we were unaware of. The interviews also provided us with more insight about the end users of the system. Another added benefit was that we were able to triangulate our results with responses in the interviews, allowing us to validate, or refute our findings.
